\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://manesioz.github.io/}{\Large Zachary Manesiotis}} & Email : \href{mailto:zack.manesiotis@gmail.com}{zack.manesiotis@gmail.com}\\
  \href{http://manesioz.github.io/}{http://manesioz.github.io/} & Mobile : +1-416-919-2203 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Engineering in Electrical and Computer Engineering - Dean's Honour List}{Sept. 2017 - May 2022}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Geotab}{Oakville, ON}
      {Data Engineering Intern}{May 2019 - Present}
      \resumeItemListStart
        \resumeSubItem{}
          {Developed, orchestrated, and managed performant, scalable, and distributed ETL pipelines which streamed petabytes of geospatial data from \textgreater 1 Million vehicles daily using Python, Apache Airflow, Beam, and Google Cloud Platform.} 
        \resumeSubItem{}
          {Built a performant, distributed messaging system using Google Cloud Pub/Sub, Cloud Function, and Node.js.} 
        \resumeItem{}
          {Took initiative to develop CI/CD pipelines from scratch using Gitlab-CI for small teams, increasing code quality and coverage by over 40\%.}
        \resumeItem{}
          {Developed an end-to-end automated data quality monitoring service using Apache Airflow and GCP (BigQuery, Cloud Pub/Sub, Kubernetes Engine) which enabled teams to identify the underlying firmware issues.}
        \resumeItem{}
          {Dynamically managed and allocated infrastructure with scripts and Google Kubernetes Engine to optimize use, saving hundreds of dollars per month by eliminating inefficient use of resources.}
        \resumeItem{}
          {Used Python and various data visualization libraries (MapBoxGL, Matplotlib, Brancas, Dash) to develop custom examples and tutorials on data.geotab.com to encourage users to explore open data.}
        \resumeItem{}
          {Leveraged OpenStreetMap data and other open-source tools to develop actionable insights for city planners and other government agencies.}
        \resumeItem{}
          {Assisted with feature-engineering, data cleaning, and development of Random Forest classifiers which helped clients identify key factors affecting vehicle battery health.}
        \resumeItem{}
          {Collaborated with business and product teams to develop a data-driven 2-tiered pricing scheme for clients.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Secure Graphene:}
      {Extended the open-source project Graphene, which is a library for making GraphQL APIs in Python, by providing out-of-the-box solutions for securing your API against malicious queries (for example, query depth limiting).}
    \resumeSubItem{Cartography:}
      {Contributing to Lyft's open-source project by adding Google Cloud Storage Bucket ingestion and subsequently consolidating it's infrastructure assets and relationships in a Neo4j database.}
    \resumeSubItem{Networkx:}
      {Contributed to the open-source project Networkx by revising error messages and string formatting according to Python best-practices.}
    \resumeSubItem{Music in Motion:}
      {Developed a gesture-controlled music player which integrates ultrasonic sensors with Spotify's API.}
    \resumeSubItem{Mars Rover Team:}
      {Assisted in the architecture and development of the vision and path-planning systems of an autonomous rover. Development was in a Linux environment using Python and ROS.}
    \resumeSubItem{iGEM:}
      {Developed mathematical models and visualizations for McMaster University's Synthetic Biology team.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages:}
      {Python, SQL, Java, C, HTML/CSS, JavaScript, Go, Bash}
    \resumeSubItem{Technologies:}
      {Git, Apache Airflow \& Beam, Google Cloud Platform, JIRA, Kafka, ElasticSearch}
    \resumeSubItem{Frameworks/Libraries:}
      {Django, Graphene, Pandas, Numpy, Scipy, Scikit-learn, Networkx, Matplotlib, Selenium}
%   \item{
%      \textbf{Languages}{: Python, Java, SQL, C}
%      \hfill
%      \textbf{Technologies}{: GCP (BigQuery, GCE, Cloud Scheduler, etc), Apache Airflow, Docker, GraphQL, Kafka}
%   }
%\textbullet \hspace{3pt}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
